LAGOS lake depth

### 2019-10-14 lagos_depth.Rmd
fig cleanup

plot_grid(
ggplot(data = hypso_ct) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = id)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") + 
  ggtitle(paste0("CT", " (", length(unique(hypso_ct$id)), ") lakes")) + 
  theme(legend.position = "bottom"), 
ggplot(data = hypso_mn) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = llid)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") +
  ggtitle(paste0("MN", " (", length(unique(hypso_mn$llid)), ") lakes")) +
  theme(axis.title.y = element_blank(), 
        legend.position = "none"), 
rel_widths = c(1, 0.7))

@@

rsub1 <- raster::raster("data/ct_bathy/pickerel_lake.tif")
rsub2 <- raster::raster("data/ct_bathy/long_pond.tif")

if(!(file.exists("data/elevatr/pickerel_lake.gri") & 
     file.exists("data/elevatr/long_pond.gri"))){
  elev <- get_elev_raster(rsub1, 13)
  raster::writeRaster(elev, paste0("data/elevatr/", names(rsub1)))

  elev <- get_elev_raster(rsub2, 13)
  raster::writeRaster(elev, paste0("data/elevatr/", names(rsub2)))
}
elev1 <- raster::raster("data/elevatr/pickerel_lake.gri")
elev2 <- raster::raster("data/elevatr/long_pond.gri")

@@

sphere_shade(res_rsub1$rmat, texture = tex) %>%
  plot_3d(res_rsub1$rmat, water = TRUE, waterdepth = res_rsub1$maxdepth,
          zscale = 0.4, solidcolor = "white", solidalpha = 0.4,
          shadow = FALSE, solidlinecolor = "white", phi = 10, theta = -20)
render_snapshot("figures/concave-rayshader.png", clear = TRUE)

@@

sphere_shade(res_rsub2$rmat, texture = tex) %>%
  plot_3d(res_rsub2$rmat, water = TRUE, waterdepth = res_rsub2$maxdepth,
          zscale = 0.4, solidcolor = "white", solidalpha = 0.4,
          shadow = FALSE, solidlinecolor = "white", phi = 10, theta = -20)
render_snapshot("figures/convex-rayshader.png", clear = TRUE)

@@

```{r get-hypso, eval=TRUE, fig.height = 4}
rsub1 <- raster::raster("data/ct_bathy/pickerel_lake.tif")
rsub2 <- raster::raster("data/ct_bathy/long_pond.tif")
names(rsub1) <- "layer"
names(rsub2) <- "layer"

get_hypso <- function(rsub, id){
  maxdepth <- abs(cellStats(rsub, "max"))

@@

```{r workflow}
gg_radius_convex <- 
  ggplot(data = dplyr::filter(hypso, type == "convex"), 
         aes(x = radius_percent, y = depth)) +
    geom_point() + geom_line() +
    xlab("Radius distance (proportion)") + ylab("Depth") +
    scale_y_reverse()

@@

cowplot::plot_grid(
  gg_convex_raster, 
  ggdraw() +
  draw_image("figures/convex-rayshader.png"),
  gg_radius_convex, 
  gg_hypso_convex, 
  ncol = 1
)
```

>>>>

gg_hypso_ct <- ggplot(data = hypso_ct) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = llid)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") + 
  ggtitle(paste0("CT", " (", length(unique(hypso_ct$llid)), ") lakes")) + 
  theme(legend.position = "bottom")

gg_hypso_mn <- ggplot(data = hypso_mn) +
  geom_polygon(data = polys, aes(x = x, y = y, group = id, fill = id), alpha = 0.2) +
  geom_line(aes(x = area_percent, y = depth_percent, group = llid)) +
  geom_abline(intercept = -100, slope = 1, color = "red") +
  ylim(c(100, 0)) +
  ylab("Depth (percent)") + xlab("Area (percent)") +
  ggtitle(paste0("MN", " (", length(unique(hypso_mn$llid)), ") lakes")) +
  theme(axis.title.y = element_blank(), 
        legend.position = "none")

plot_grid(gg_hypso_ct, gg_hypso_mn, 
rel_widths = c(1, 0.7))

gg_hypso_ct + theme(plot.title = element_blank())

@@

# "pickerel_lake" 7096 # convex
# "long_pond" 99642 # concave
rsub1 <- raster::raster("data/ct_bathy/7096.tif")
rsub2 <- raster::raster("data/ct_bathy/99642.tif")

if(!(file.exists("data/elevatr/7096.gri") & 
     file.exists("data/elevatr/99642.gri"))){
  elev <- get_elev_raster(rsub1, 13)
  raster::writeRaster(elev, paste0("data/elevatr/", 
                                   gsub("X", "", names(rsub1))
                                   ))

  elev <- get_elev_raster(rsub2, 13)
  raster::writeRaster(elev, paste0("data/elevatr/", 
                                   gsub("X", "", names(rsub2))
                                   ))
}
# "pickerel_lake" 7096 # convex
# "long_pond" 99642 # concave
elev1 <- raster::raster("data/elevatr/7096.gri")
elev2 <- raster::raster("data/elevatr/99642.gri")

@@

sphere_shade(res_rsub1$rmat, texture = tex) %>%
  plot_3d(res_rsub1$rmat, water = TRUE, waterdepth = res_rsub1$maxdepth,
          zscale = 0.4, solidcolor = "white", solidalpha = 0.4,
          shadow = FALSE, solidlinecolor = "white", phi = 10, theta = -20)
render_snapshot("figures/concave-rayshader.png", clear = TRUE)
magick::image_read("figures/concave-rayshader.png") %>%
  magick::image_trim() %>%
  magick::image_write("figures/concave-rayshader.png")

@@

sphere_shade(res_rsub2$rmat, texture = tex) %>%
  plot_3d(res_rsub2$rmat, water = TRUE, waterdepth = res_rsub2$maxdepth,
          zscale = 0.4, solidcolor = "white", solidalpha = 0.4,
          shadow = FALSE, solidlinecolor = "white", phi = 10, theta = -20)
render_snapshot("figures/convex-rayshader.png", clear = TRUE)
magick::image_read("figures/convex-rayshader.png") %>%
  magick::image_trim() %>%
  magick::image_write("figures/convex-rayshader.png")

@@

```{r get-hypso, eval=TRUE, fig.height = 4}
# "pickerel_lake" 7096 # convex
# "long_pond" 99642 # concave
rsub1 <- raster::raster("data/ct_bathy/7096.tif")
rsub2 <- raster::raster("data/ct_bathy/99642.tif")
names(rsub1) <- "layer"
names(rsub2) <- "layer"

get_hypso <- function(rsub, llid){
  maxdepth <- abs(cellStats(rsub, "max"))

@@

```{r workflow, eval=TRUE}
gg_radius_convex <- 
  ggplot(data = dplyr::filter(hypso, type == "convex"), 
         aes(x = radius_percent, y = depth)) +
    geom_point() + geom_line() +
    xlab("Radius distance (proportion)") + ylab("Depth") +
    scale_y_reverse()

@@

cowplot::plot_grid(
  gg_convex_raster + theme(plot.title = element_blank()), 
  ggdraw() +
  draw_image("figures/convex-rayshader.png"),
  gg_radius_convex, 
  gg_hypso_convex, 
  ncol = 2, nrow = 2
)
```
